---
title: "Seminar 2b"
author: "Louis-Alexandre Fournier"
date: "January 8, 2018"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#STAT 540 Seminar 2B

#Part 1 - First time ggplot-ing

```{r tidyverse}
library(tidyverse)
```

###Do cars with big engines use more fuel than cars with small engines? 
####mpg dataset
```{r mpg dataframe}
mpg
```
####Highway miles per gallon in function of engine displacement (L)
```{r ggplot of mpg}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```

```{r barebones graphing template}
ggplot(data = mpg) + geom_smooth(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg) + geom_density_2d(mapping = aes(x = displ, y = hwy))
```

####City miles per gallon in function of engine displacement (L)
```{r ggplot of mpg for cty}
ggplot(data = mpg) + geom_point(mapping = aes(x= displ, y = cty))
```

####Aestethic mappings
#####color
```{r aesthetic color}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

#####size
```{r aesthetic size}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = class))
```

#Part 2 - The layered Grammar
##Smooth line
###Regression of Highway miles per gallon as a function of engine displacement(L)

```{r smooth line}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_point() + geom_smooth()
```

##continuous variable in the 3rd dimension
###Regression of Highway miles per gallon as a function of engine displacement(L) with color points by year
```{r regression year}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = year)) + geom_point() + geom_smooth()
```

###Regression of Highway miles per gallon as a function of engine displacement(L) with color points by transmission
```{r regression trans}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = trans)) + geom_point() + geom_smooth()
```

##bar chart
### Average fuel efficiencies for each vehicle class
```{r average fuel efficiency by class}
(averageEfficiency <- mpg %>% group_by(class) %>% summarise(fuel_efficiency = mean(hwy)))
ggplot(averageEfficiency) + geom_bar(aes(x = class, y = fuel_efficiency, fill = class), stat = "identity") + ylab("Fuel Efficiency (miles per gallon)") + xlab("Vehicle Type")
```

### Average fuel efficiencies for each vehicle class - SCALE REVERSED
```{r average fuel efficiency by class - REVERSED}
(averageEfficiency <- mpg %>% group_by(class) %>% summarise(fuel_efficiency = mean(hwy)))
ggplot(averageEfficiency) + geom_bar(aes(x = class, y = fuel_efficiency, fill = class), stat = "identity") + ylab("Fuel Efficiency (miles per gallon)") + xlab("Vehicle Type") + scale_y_reverse()
```

###Coordinate function
####flip
```{r average fuel efficiency by class - Coordinate flip}
(averageEfficiency <- mpg %>% group_by(class) %>% summarise(fuel_efficiency = mean(hwy)))
ggplot(averageEfficiency) + geom_bar(aes(x = class, y = fuel_efficiency, fill = class), stat = "identity") + coord_flip()
```

####polar
```{r average fuel efficiency by class - Coordinate polar}
(averageEfficiency <- mpg %>% group_by(class) %>% summarise(fuel_efficiency = mean(hwy)))
ggplot(averageEfficiency) + geom_bar(aes(x = class, y = fuel_efficiency, fill = class), stat = "identity") + coord_polar()
```

###Facet Function
```{r facet function}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +geom_point() + facet_wrap(~class)
```

#Part 3: Deliverable
###Regression of Highway miles per gallon as a function of engine displacement(L) with color points by transmission
```{r deliverable seminar2b}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv, size = class)) + geom_point() 
```